---
title: "Monte Carlo - Simlation package"
author: "By Anders Højrup, Markus Legat & Christian Skalborg Jensen"
date: 'November 2019'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
# Functions included in the package

```{r, echo = FALSE}
library(ACM)
```

## ARsim( )
The function `ARsim()` draws from the random variable, which is specified by the density $f$, using acceptance rejection sampling. 
The default proposal density is the exponential density with rate 1. If you want to use a different density you have to set the argument "exponential" to FALSE and specify your new proposal density and the corresponding inverse distribution function. Don't forget to find an appropriate $C$ such that $f(x) \leq C*g(x)$.

Let's look at an example:
```{r}
C <- 1.6
lambda <- 0.5
f <- function(x) {x*exp(-x)}

ARsimulation <- ARsim(f, C, 100000, rate = lambda)
```

The class of output of `ARsim()` is "AR". We therefore added sepecified methods for plotting and also a summary function.


```{r fig3, fig.width = 8, fig.asp = .62}
plot(ARsimulation, ggplot = TRUE)
summary(ARsimulation)
```



## inv_sample( )
The function inv_sample() draws from the random variable, which is specified by the distribution F, using inverse sampling. 

## int( )
The function int() performs a Monte Carlo integration of the function f.


## plot.copula( )
plot.copula() plots a 2 dimensional copula, using empirical CDF.

## plot.invsample( )
The function plot.invsample() plots the empirical distribution function of the sampled values

## plot.MC_integral( )
The function plot.MC_integral plots the integrand of a corresponding MC integration 

## plot.simulation( )
Generates the plot of the mean and confidence interval.

## rbi_norm( )
Generates a bivariate normal distribution

## Simulation_analysis( )
Creates a simple PDF analysis for a simulation vector. PDF is saved in current working directory

## summary.invsample( )
Summary method for inverse sampling

## summary.MC_integral( )
Summary method for Monte Carlo integrals

## summary.simulation( )
Returns a list of mean, variance, relative error and confidence interval.


